No Detectable Evidence of Genetic Associations with Anadromous and Resident Masu Salmon Sampled within Hokkaido

### 2022-08-31 paper/paper_draft.Rmd
MASU draft

---
title: "No Detectable Evidence of Genetic Associations with Anadromous and Resident Masu Salmon Sampled within Hokkaido"
author: "William Hemstrom"
date: "11/21/2021"
output:
  word_document:
    reference_docx: "style_ref.docx"
  pdf_document:
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    fig_width: 7
    fig_height: 6
bibliography: "MASU_Paper_References.bib"
csl: "council-of-science-editors-author-date.csl"
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{setspace}\doublespacing
  - \usepackage{sectsty}\sectionfont{\fontsize{12}{12}\selectfont}
  - \usepackage{sectsty}\subsectionfont{\normalfont\itshape\fontsize{12}{12}\selectfont}
  - \usepackage[round]{natbib}
indent: true
sansfont: Times New Roman
fontsize: 12pt
---

@@

Masu salmon (Oncorhynchus masou, otherwise known as cherry salmon) have the most limited distribution among the Pacific salmon. Since they spend a greater portion of their life in freshwater rivers or streams than most other migratory salmon, they are particularly exposed to fishing and sportfishing pressures [@Miyakoshi2009]. Their increased vulnerability makes it critical to understand the details that influence and control migratory life history variance in the species. Masu in particular (like steelhead salmon/rainbow trout Oncorhynchus mykiss and other species to a lesser degree) are partially migratory, with large resident and anadromous populations [@Morita2014]. As is typical, anadromous masu are initially born in the rivers then migrate to the seas where they develop larger body sizes, then eventually migrate back to their natal rivers in order to breed [@Dodson2013]. Resident masu in contrast sexually mature at a younger age and stay within the river systems throughout their entire lives [@Morita2010].

The decision to migrate in masu salmon is thought to be primarily influenced by environmental factors such as temperature alongside other factors such as the salmon's body size, growth rate, lipid stores, and is heavily sex influenced [@Morita2014; @Arostegui2019]. Migration and residency in the closely related steelhead salmon (Oncorhynchus mykiss) are controlled by similar factors. For example, resident steelhead tend to be larger within the first few months of life when compared to anadromous individuals (Morita et al., 2014). Of course, differences in environmental factors can influence growth rates and therefore also migration in steelhead. For example, during poor nutrient conditions, a higher proportion of individuals than expected from genetics may be anadromous; whereas during flooding or nutrient rich periods, a higher proportion of resident individuals may be observed [@Kelson2020]. Regardless of environmental conditions, however, those individuals within a population which grow faster as juveniles are more likely to stay as residents than otherwise, even under similar conditions [@Kendall2015].

Migration comes with a tradeoff. In steelhead, migratory juveniles tend to have low survival rates to adulthood, which is  compensated for by the high fecundity of anadromous females that can significantly exceed that of residents [@Pearse2019]. This pattern likely holds true for masu as well (Morita et al., 2014). This trade-off is not as pronounced in male steelhead, which can mature as early as freshwater residents, avoiding the high mortality associated with migration [@Pearse2019]. This results in greater frequency of anadromy in females; a trend also seen in masu salmon (Morita et al., 2014). Consequently, changes in environmental factors, such as those caused by climate change, have been known to impact the decision of the masu to be either resident or anadromous [@Morita2014]. For example, Morita et al (2014) has shown that the number of resident males have increased while the proportion of anadromous males and the proportion of delayed migrants within both females and males have decreased as temperatures have increased over time, leading to a significant decrease in the overall number of anadromous individuals.

In contrast to environmental factors, the genetic factors that contribute to migration in masu salmon have not been well studied. Despite the prevalence of environmental control of migration in masu, it is not unreasonable to expect genetic elements to play some role in governing migratory decisions in the species. For example, within steelhead, there is strong evidence suggesting both an environmental and genetic basis for migratory life history. In 1944, Naeve conducted common garden and transplant experiments with sympatric rainbow trout and steelhead and found that migratory status was heritable after observing that rainbow trout offspring were considerably more likely to be resident themselves, whereas crosses between anadromous individuals resulted in the most anadromous smolts. Indeed, recent studies have found that  the decision to migrate in steelhead is strongly linked to a large genomic inversion on chromosome Omy5 throughout their geographic range which seems to maintain a set of linked genes that controls migratory behavior [@Arostegui2019; @Kelson2020; @Pearse2014). The genetic basis for migration is also likely indirectly mediated by physiological characteristics such as growth rate, which are also known to be influenced by the same large genetic elements that differ between anadromous and resident individuals [@Miller2021]. Taken together, it seems clear that migration in steelhead is jointly controlled by the interplay of genetic and environmental factors.

>>>>

---
title: "No Detectable Evidence of Genetic Associations with Anadromous and Resident Masu Salmon Sampled within Hokkaido"
author: "William Hemstrom"
date: "11/21/2021"
output:
  word_document:
    reference_docx: "style_ref.docx"
  pdf_document:
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    fig_width: 7
    fig_height: 6
bibliography: "MASU_Paper_References.bib"
csl: "molecular-ecology.csl"
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{setspace}\doublespacing
  - \usepackage{sectsty}\sectionfont{\fontsize{12}{12}\selectfont}
  - \usepackage{sectsty}\subsectionfont{\normalfont\itshape\fontsize{12}{12}\selectfont}
  - \usepackage[round]{natbib}
indent: true
sansfont: Times New Roman
fontsize: 12pt
---

@@

Masu salmon (Oncorhynchus masou, otherwise known as cherry salmon) have the most limited distribution among the Pacific salmon [@augerot2005atlas]. Since they spend a greater portion of their life in freshwater rivers or streams than most other migratory salmon, they are particularly exposed to fishing and sportfishing pressures [@Miyakoshi2009]. Their increased vulnerability makes it critical to understand the details that influence and control migratory life history variance in the species. Masu in particular (like steelhead salmon/rainbow trout Oncorhynchus mykiss and other species to a lesser degree) are partially migratory, with large resident and anadromous populations [@Morita2014]. As is typical, anadromous masu are initially born in the rivers then migrate to the seas where they develop larger body sizes, then eventually migrate back to their natal rivers in order to breed [@Dodson2013]. Resident masu in contrast sexually mature at a younger age and stay within the river systems throughout their entire lives [@Morita2010].

The decision to migrate in masu salmon is thought to be primarily influenced by environmental factors such as temperature alongside other factors such as the salmon's body size, growth rate, lipid stores, and is heavily sex influenced [@Morita2014; @Arostegui2019]. Migration and residency in the closely related steelhead salmon (Oncorhynchus mykiss) are controlled by similar factors. For example, resident steelhead tend to be larger within the first few months of life when compared to anadromous individuals [@Morita2014]. Of course, differences in environmental factors can influence growth rates and therefore also migration in steelhead. For example, during poor nutrient conditions, a higher proportion of individuals than expected from genetics may be anadromous; whereas during flooding or nutrient rich periods, a higher proportion of resident individuals may be observed [@Kelson2020]. Regardless of environmental conditions, however, those individuals within a population which grow faster as juveniles are more likely to stay as residents than otherwise, even under similar conditions [@Kendall2015].

Migration comes with a tradeoff. In steelhead, migratory juveniles tend to have low survival rates to adulthood, which is  compensated for by the high fecundity of anadromous females that can significantly exceed that of residents [@Pearse2019]. This pattern likely holds true for masu as well [@Morita2014]. This trade-off is not as pronounced in male steelhead, which can mature as early as freshwater residents, avoiding the high mortality associated with migration [@Pearse2019]. This results in greater frequency of anadromy in females; a trend also seen in masu salmon [@Morita2014]. Consequently, changes in environmental factors, such as those caused by climate change, have been known to impact the decision of the masu to be either resident or anadromous [@Morita2014]. For example, Morita et al [-@Morita2014] has shown that the number of resident males have increased while the proportion of anadromous males and the proportion of delayed migrants within both females and males have decreased as temperatures have increased over time, leading to a significant decrease in the overall number of anadromous individuals.

In contrast to environmental factors, the genetic factors that contribute to migration in masu salmon have not been well studied. Despite the prevalence of environmental control of migration in masu, it is not unreasonable to expect genetic elements to play some role in governing migratory decisions in the species. For example, within steelhead, there is strong evidence suggesting both an environmental and genetic basis for migratory life history. In 1944, Naeve conducted common garden and transplant experiments with sympatric rainbow trout and steelhead and found that migratory status was heritable after observing that rainbow trout offspring were considerably more likely to be resident themselves, whereas crosses between anadromous individuals resulted in the most anadromous smolts [double check paper that this was in]. Indeed, recent studies have found that  the decision to migrate in steelhead is strongly linked to a large genomic inversion on chromosome Omy5 throughout their geographic range which seems to maintain a set of linked genes that controls migratory behavior [@Arostegui2019; @Kelson2020; @Pearse2014]. The genetic basis for migration is also likely indirectly mediated by physiological characteristics such as growth rate, which are also known to be influenced by the same large genetic elements that differ between anadromous and resident individuals [@MILLER2012]. Taken together, it seems clear that migration in steelhead is jointly controlled by the interplay of genetic and environmental factors.
